Learning \strips\ action models with classical planning

### 2018-02-22 doc/aij18/aij18.tex
updates added to aij18 paper

@@

Our interest when computing the {\em observation edit distance} is not in $\mathcal{M}'$ but in the number of required {\em edit operations} for that $\mathcal{M}'$ is validated in the given observations, e.g. $\delta(\mathcal{M},\mathcal{O})=2$ for the example in Figure~\ref{fig:plan}. The {\em observation edit distance} is exactly computed if $P_{\Lambda}'$ is optimally solved (according to the number of edit actions); is approximated if $P_{\Lambda}'$ is solved with a satisfying planner (our case); and is a less accurate estimate (but faster to be computed) if the solved task is a relaxation of $P_{\Lambda}'$~\cite{bonet2001planning}.

\begin{figure}
{\tt\small
00 : (insert\_add\_handempty\_stack)\\
01 : (insert\_add\_clear\_stack\_var1)\\
02 : (apply\_unstack block2 block1)\\
03 : (validate\_1)\\
04 : (apply\_putdown block2)\\
05 : (validate\_2)\\
06 : (apply\_pickup block1)\\
07 : (validate\_3)\\
08 : (apply\_stack block1 block2)\\
09 : (validate\_4)\\
}
 \caption{\small Plan for editing a given {\em blockswold} schema and validating it at the state observations shown in Figure~\ref{fig:lexample}.}
\label{fig:plan}
\end{figure}

\section{Evaluation}
\label{sec:Section7}
This section evaluates the performance of our approach for learning \strips\ action models starting from different amounts of available input knowledge.

@@

\section{Conclussions}
\label{sec:Section8}

>>>>

Our compilation is extensible to compute the {\em edit distance} between two models. A solution to the planning task resulting from the extended compilation is a sequence of actions that edits the action model $\mathcal{M}$ to  produce $\mathcal{M}'$ using to the two {\em edit operations}.

The output of the extended compilation is a classical planning task $P_{\Lambda}'=\tup{F_{\Lambda},A_{\Lambda}',I_{\Lambda}',G_{\Lambda}}$:

Our interest when computing the {\em observation edit distance} is not in $\mathcal{M}'$ but in the number of required {\em edit operations}, e.g. $\delta(\mathcal{M},\mathcal{O})=2$ for the example in Figure~\ref{fig:plan-edistance}. The {\em observation edit distance} is exactly computed if $P_{\Lambda}'$ is optimally solved (according to the number of edit actions); is approximated if $P_{\Lambda}'$ is solved with a satisfying planner (our case); and is a less accurate estimate (but faster to be computed) if the solved task is a relaxation of $P_{\Lambda}'$~\cite{bonet2001planning}.

\begin{figure}[hbt!]
{\tt\small
00 : (insert\_add\_handempty\_stack)\\
01 : (insert\_add\_clear\_stack\_var1)
}
 \caption{\small Plan for editing a given {\em blockswold} schema and validating it at the state observations shown in Figure~\ref{fig:lexample}.}
\label{fig:plan-edistance}
\end{figure}

\subsection{Computing the observations distance}

@@

Our interest when computing the {\em observation edit distance} is not in $\mathcal{M}'$ but in the number of required {\em edit operations} for that $\mathcal{M}'$ is validated in the given observations, e.g. $\delta(\mathcal{M},\mathcal{O})=2$ for the example in Figure~\ref{fig:plan-odistance}. The {\em observation edit distance} is exactly computed if $P_{\Lambda}'$ is optimally solved (according to the number of edit actions); is approximated if $P_{\Lambda}'$ is solved with a satisfying planner (our case); and is a less accurate estimate (but faster to be computed) if the solved task is a relaxation of $P_{\Lambda}'$~\cite{bonet2001planning}.

\begin{figure}[hbt!]
{\tt\small
00 : (insert\_add\_handempty\_stack)\\
01 : (insert\_add\_clear\_stack\_var1)\\
02 : (apply\_unstack block2 block1)\\
03 : (validate\_1)\\
04 : (apply\_putdown block2)\\
05 : (validate\_2)\\
06 : (apply\_pickup block1)\\
07 : (validate\_3)\\
08 : (apply\_stack block1 block2)\\
09 : (validate\_4)\\
}
 \caption{\small Plan for editing a given {\em blockswold} schema and validating it at the state observations shown in Figure~\ref{fig:lexample}.}
\label{fig:plan-odistance}
\end{figure}

\section{Recognition of \strips\ action models}
\label{sec:Section7}

\section{Evaluation}
\label{sec:Section8}
This section evaluates the performance of our approach for learning \strips\ action models starting from different amounts of available input knowledge.

@@

\section{Conclussions}
\label{sec:Section9}
